---
title: "Visualization Pt 1"
author: "Xue Yang"
date: "9/27/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```


```{r}
library(tidyverse)
library(ggridges)
```

```{r data_import, cache = TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df

# weather_df %>% View
```


## Start a plot

Blank plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```



Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point()
```

Scatterplot for a part of the data

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Name the scatterplot

```{r}
weather_sp =
  ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```


## More plot options

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name))
```

Add a geom_smooth

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

Add a geom_smooth which there is no confidence interval around smooth

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth(se = FALSE)
```

Add a geom with alpha = 0.4

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.4) +
  geom_smooth(se = FALSE)
```

Add a geom with point and smooth colored by name

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se = FALSE)
```

can also colored by prcp

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = prcp)) +
  geom_point(alpha = 0.4) 
```

Facetting with name

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se = FALSE) +
  facet_grid( ~ name)
```



A more interesting plot

change the x and y aes

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) +
  geom_point()
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) +
  geom_line()
```

add "size" 

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name, size = prcp)) +
  geom_point()
```

altogether

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name, size = prcp)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid( ~ name)
```

keep in mind of the differences between these two:


```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")  # true
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))  # flase
```

## Univariate plots

Histograms!!

```{r}
ggplot(weather_df, aes(x = tmax)) +
  geom_histogram()
```

```{r}
ggplot(weather_df, aes(x = tmax)) +
  geom_histogram() +
  facet_grid(~name)
```

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) +
  geom_histogram()
```

Density

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) +
  geom_density(alpha = 0.5)
```

Boxplot!!

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) +
  geom_boxplot()
```


Violin plot!

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) +
  geom_violin()
```

density ridges!

```{r}
ggplot(weather_df, aes(x = tmax, y = name)) +
  geom_density_ridges()
```

```{r}
ggplot(weather_df, aes(x = prcp, y = name)) + 
  geom_density_ridges(scale = .85)
```

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)

```


## Last example

Make a bunch if plots!

```{r}
ggplot(weather_df, aes(y = prcp, x = name))+
  geom_boxplot()
```

```{r}
ggplot(weather_df, aes(y = prcp, x = name))+
  geom_violin()
```

```{r}
ggplot(weather_df, aes(x = prcp, fill = name))+
  geom_density(alpha = .5)
```

```{r}
weather_df %>% 
  filter(prcp <100) %>% 
  ggplot(aes(x = prcp, fill = name))+
  geom_density(alpha = .5)
```


```{r}
weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name))+
  geom_density(alpha = .5)
```

